---
title: "Absorbed radiance and leaf to air temperature difference simulation"
author: "Wen Lin"
date: "June 21, 2017"
output: word_document
---
# Contents

1. simulate absorbed radiance
2. simulate leaf-to-air temperature difference 

## 1. Simulation of absorbed radiance 
```{r setup}
tao <- 0.7 # atmopheric transmittance. the values are between 0.6 and 0.7 for clear conditions
phi <- 5/180*pi   # sun zenith angle (5 degrees)
m <- exp(-625*0.3048/8200)/cos(phi) # optical air mass number 
Sp <- 1360*tao^m        # direct radiation
Sd <- 0.3*(1-tao^m)*1360*cos(phi)   # diffuse radiation 
Fp <- cos(phi)/2 # view factor for direct radiation
St <- Fp*Sp+Sd  # global irradiance for calculating reflected radiation 
albedo <- 0.1 # evergreen conifer conifer albedo: 0.08-0.11. 
Sr <- albedo*St  # reflected radiation 

alpha_s <- 0.88 # conifer absorptivity for solar wavebands, value is from Martin's paper
alpha_l <- 0.96 # conifer absorptivity for thermal wavebands, value is from Martin's paper

T_a <- 35 # air temperature
B <- 5.67E-8 * (T_a+273.15)^4# black body emittance 

e_c <- 9.2E-6*(T_a+273.15)^2  # clear sky emissivity

# F: view factors
Fd <- Fr <- Fa <- Fg <- 0.5

La <- e_c* B # long wave flux density from the atmophere
Lg <- La # long wave flux density from the ground, assuming ground temperature is equal to air temperature

# absorbed radiance
R_abs <- alpha_s*(Fp*Sp+Fd*Sd+Fr*Sr)+alpha_l*(Fa*La+Fg*Lg);
R_abs <- round(R_abs,0)
paste0("Absorbed radiance at minimal sun zenith angle = ",R_abs," W/m2")
```

## 2. Simulation of leaf-to-air temperature difference
```{r}
# global variable: wind speed (u)
u <- seq(0.1,5,l=100)

# function to calculate saturated vapor pressure
vp3 <- function(Tmpt) # unite: kpa formula source: Campbell&Norman Env. biophysics
{return(0.611*exp((17.502*Tmpt)/(Tmpt+240.97)))}

# the slope of the saturation vapor pressure function
Delta.fun <- function(x)
{return(17.502*240.47*vp3(x)/(240.97+x)^2)}

# function to simulate leaf to air temperature difference
leaf.T.R <- function(R_abs)
{
  g_vs <- 0.067 # stomatal conductance
  RH <- 0.50 # RH: relative humidity
  T_a <- 35 # T_a: air temperature
  width <- 1.5E-3 # leaf diameter: 1.5mm
  
  gamma <- 6.66E-4 # thermodynamic psychrometer constant
  # calculate the atmospheric pressure of the site with elevation as 191m
  p_a <- 101.3*exp(-191/8200)
  c_p <- 29.3 # specific heat of air at constant pressure, unit J/mol/K
  
  B <- 5.67E-8 * (T_a+273.15)^4
  # g_r: radiative conductance at air temperature, simulated using a polynomial function
  g_r <- 7E-6*(T_a+273.15)^2-0.0021*(T_a+273.15)+0.2085;g_r 
  
  e_s <- vp3(T_a); # e_s: saturated vapor pressure at air temperature = 35C
  Delta <- Delta.fun(T_a) # Delta: slope of vapor pressure function at air temperature = 35C
  s <- Delta/p_a;s # s: slope of saturation mole fraction function
  D <- e_s*(1-RH) # D: VPD
  R_ni <- R_abs - B*0.97
  
  d <- 0.7*width # d: leaf characteristic dimension
  # g_Ha: boundary layer conductance for heat, 1.4 is used for outdoor conditions
  g_Ha <- 1.4*0.135*sqrt(u/d)
  # g_va: boundary layer conductance for vapor, 1.4 is used for outdoor conditions
  g_va <- 1.4*0.147*sqrt(u/d)
  g_Hr <- g_Ha+g_r # g_Hr: sum of boundary layer and radiative conductances
  g_v <- (g_vs*g_va)/(g_vs+g_va);g_v # assume abaxial and adaxial conductance to be the same
  gamma_star <- gamma *g_Hr/g_v;gamma_star # gamma_star: apparent psychrometer constant
  #T_d: the air to leaf temperature difference 
  T_d <- gamma_star/(gamma_star+s)*(R_ni/(g_Hr*c_p)-D/p_a/gamma_star)
  return(T_d)
}

dat <- data.frame(T1=leaf.T.R(0),T2=leaf.T.R(300), T3=leaf.T.R(600), T4=leaf.T.R(928))
par(mar=c(4.5,5,1,1))
matplot(u,dat,type="l",col=rainbow(4),lty=1,
        ylab=expression(T[l]~"-"~T[a]~"("~degree*C~")"),xlab="Wind speed (m/s)")
abline(h=0,col=8,lty=3)
text(0.5,4,pos=4,expression(T[a]*"=35"*degree*C*", RH=50%, "*g[s]*"=67mmol"~m^{-2}~s^{-1}),cex=0.8)
legend("bottomright",expression(R[abs]*"= 0 W"~m^{-2},R[abs]*"= 300 W"~m^{-2},R[abs]*"= 600 W"~m^{-2},R[abs]*"= 928 W"~m^{-2}),lty=1,col=rainbow(4),cex=0.8,ncol=2)
```
$$ g_{Hr}= g_{Ha}+g_r$$
$$ g_{Ha}=1.4*0.135*\sqrt{\frac{u}{d}}$$
Where u represents wind speed, and d represents leaf characteristic dimension. 1.4 is used because of outdoor conditions. 
$$ d=0.7*leaf diameter $$

$ g_r $ is obtained from a table from Appendex. The table shows that $ g_r $ is a function of temperature. Thus I used a polynomial function to simulate $ g_r $ using temperature. 